### 2020-01-20 methods.tex
added org sec

----

>>>>

\paragraph{Organization of this paper}

We want to study the effective of Product Norm Metrics in describing trends in the
generalization accuracyof real-word, production quality, pretrained Deep Neural Networks.
In Section \ref{sxn:cv}, we study three well known, and widely available DNN CV architectures:
the VGG series, the ResNet series, and the DenseNet series of models.  We lay out the
basic methodology we use to evaluate the different metrics against the reported test accuracies. 
We also introduce the notion of Correlation Flow, compare the three pretrained architectures in detail.  
In Section  \ref{sxn:nlp}, we then look at several variations of a popular NLP DNN architecture,
the OpenAI GPT and GPT2 models.  We discuss when and how the different metrics apply more generally.
Finally, in Section \ref{sxn:all}, we examine over 100 pretraind DNN CV models, and show
how well each metric is correlated with the reported test accuracies across different models
in an architeture series.  
----
